---
title: "Data Exercise 1: Decision Making"
author: "Maanav Choudhary"
date: "`rSys.Date()"
output: html_notebook
---

#Loading Libraries and data
```{r}
library(tidyverse)
```


```{r}
data_set <- read_csv("CogSci412_DE1_data.csv") %>%
  mutate(condition = case_when(is.na(FL_39_DO) == FALSE~FL_39_DO, #First Case
                                is.na(FL_43_DO) == FALSE ~ FL_43_DO)) %>%#Second Case 
  filter(Progress == 100 & DistributionChannel == "anonymous") %>%
  select(ResponseId, condition, familiarity = Q10, pencil_control = 'Pencil Control',
         pencil_control_conf = 'Conf. Pencil Control',
         mag_stnd = 'Magazine Standard',
         mag_stnd_conf = 'Conf. Mag. Stand.',
         mag_control = Magazine_Control,
         mag_control_conf = 'Conf. Mag. Control',
         pencil_stnd = Pencil_Standard,
         pencil_stnd_conf = 'Conf. Pencil Stand.') %>%
  filter(ResponseId != "R_5R9cvvcJ5vFulLe" ) 

data_set
```

Each cell can be categroized with three pieces of info:
- pencil Vs. magazine
- control vs. standard
- answer vs. confidence

What we want in long form:

ResponseId: unique identifier for that dataset
Content: was the question about pencils or magazines
Type: was the question a control question or a standard question
DV("dependent variable"): Answer or Confidence

value: actual observed response

```{r}
data_set %>%
  pivot_longer(pencil_control:pencil_stnd_conf, names_to ="old_column", values_to = "value") %>%
  filter(is.na(value) == FALSE) %>%
  separate(into = c("content", "type", "dv"), col = old_column)
```

#For long form want one obersevation per row