---
title: "DE3"
output: html_document
author: "Maanav Choudhary"
date: "2024-11-19"
---

```{r}
#Installing dependencies
library(tidyverse)
library(ggdist)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Reading in data from the data folder

```{r}
#Descriptive data
desc <- read_csv("data/desc_all.csv") 
#Error data from trials 
e5_error <- read_csv("data/e5_error_df.csv")
e15_error <- read_csv("data/e15_error_df.csv")
e2_error <- read_csv("data/e2_error_df.csv")
```

Descriptive information on da participants

```{r}
desc %>%
  distinct(Code, group_name)
```
Box plot of descriptive information
```{r}
#Ploting data with gg plot, historgram
desc %>%
  ggplot(aes(y = no_categories)) +
  geom_histogram(binwidth = 1,
                 color = "white")
```
The above representation doesn't clearly label the different groups, nor does it outline the differences clearly. 
Use facet_grid to split up by ethnic groups

```{r}
desc %>%
  ggplot(aes(y = no_categories)) +
  geom_histogram() +
  facet_grid(~group_name)
```
Wanted to test out the differences between facet wrap and grid. This represnetaiton seems a little easier to read.
```{r}
desc %>%
  ggplot(aes(y = no_categories)) +
  geom_histogram() +
  facet_wrap(~group_name)
```
Check the ethnic groups to ensure "NA" is a mising val and not a name for an ehthnic group
```{r}
desc %>%
  distinct(group_name)
```

```{r}
desc %>%
  count(group_name)
```


Grouping data to prepare for the plot
```{r}
grouped_cat_desc <- desc %>%
  #Group by ethnicity 
  group_by(group_name) %>%
  #Get the mean of the category for the ethnic groups, also get the standaard deviation
  summarise(mean = mean(no_categories),
            sd = sd(no_categories)) %>%
  #Add a new column to data with the rounded mean and standard deviations
  mutate(mean_sd = str_c(round(mean, 2), " (", round(sd, 2), ")"))
```

```{r}
desc %>%
  filter(is.na(group_name) == FALSE) %>%
  mutate(full_group_name = case_when(group_name == "south_asian" ~ "South Asian",
                                     group_name == "se_asian" ~ "Southeast Asian",
                                     group_name == "non_asian_multi" ~ "Non-Asian Multilingual",
                                     group_name == "eng_mono" ~ "English monolingual diverse",
                                     group_name == "east_asian" ~ "East Asian"),
         full_group_name = factor(full_group_name, 
                                  levels = c("English monolingual diverse",
                                             "Non-Asian Multilingual",
                                             "South Asian",
                                             "Southeast Asian",
                                             "East Asian"))) %>%
  ggplot(aes(y = fct_rev(full_group_name),
             x = no_categories,
             fill = fct_rev(full_group_name))) +
  geom_boxplot(color = "black",
               outliers = FALSE,
               alpha = 0.8) +
  xlim(0, 20) +
  labs(x = "Number of Categories",
       y = "Group Name",
       title = "Average Number of Categories Created per group") +
  theme_minimal() +
  theme(legend.position = "none") +
  scale_fill_viridis_d(option = "plasma") +
  annotate(geom = "text", y = 1, x = 17.5, label = filter(grouped_cat_desc, group_name == "east_asian")$mean_sd) +
  annotate(geom = "text", y = 2, x = 17.5, label = filter(grouped_cat_desc, group_name == "se_asian")$mean_sd) +
  annotate(geom = "text", y = 3, x = 17.5, label = filter(grouped_cat_desc, group_name == "south_asian")$mean_sd) +
  annotate(geom = "text", y = 4, x = 17.5, label = filter(grouped_cat_desc, group_name == "non_asian_multi")$mean_sd) +
  annotate(geom = "text", y = 5, x = 17.5, label = filter(grouped_cat_desc, group_name == "eng_mono")$mean_sd)
```

