---
title: "The Effect of Cues on Memory"
output: ioslides_presentation
date: "2024-12-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggplot2)
```

## Research Questions:

- Big Question: How does prediction error affect the reactivation and reconsolidation of memories?
- Using a combination of data from both studies would yield information on how the prediction error of cues affects participant accuracy.
-
- Fork Question: Does the duration and arousal of the cues affect prediction error?
- Trying to break down the cues into features and seeing how they effect the surprise of participants.

## Method and Data Source:

- The data I used for this was from an experiment on people from various backgrounds. Varying ethnicity, gender, education level and more. 
- In the first study participants were give different types of cues and asked to rank how surprised they were by them. This surprise was used as a proxy for prediction error, and the prediction error of these cues was set as a norm.
- The second study used these cues over 3 days and evaluated the memory accuracy of participants after witnessing cues. 


```{r cars, echo = FALSE, include = FALSE}
study_1 <- read_csv("/Users/emperormaanav/Documents/COGSCI412inR/final/Study1_MoonD.csv")
```


## Slide with Plot

```{r pressure, echo=FALSE, include=FALSE}
study_2 <- read_csv("/Users/emperormaanav/Documents/COGSCI412inR/final/Data_PEMemRecon_MoonD.csv")
study_2
```


```{r}
study_1 %>%
  ggplot(aes(y = Surprise_1, fill = factor(Arousal_1))) + 
  geom_density(alpha =.5) +
  coord_flip()+  # Flips the graph vertically
  labs( title = "Density Plot of Surprise Ratings by Arousal Level", x = "Density",
    y = "Surprise Rating",  # Adjust the y-axis label (now horizontal)
    fill = "Arousal Level") +
  theme_minimal()
```

```{r plot, echo=FALSE, include=FALSE}
study_1 %>%
  ggplot(aes(y = Durationinseconds, x = Surprise_1)) + 
  geom_violin(color = "red")+
  geom_jitter(color = "lightblue", alpha = .7) +
  ylim(0,2000)
```

## Big Plot

```{r}
cueAverages <- study_2 %>%
  #group_by(List) %>%
  summarise(across(matches("^MEQ[1-9]$|^MEQ1[0-9]$"), ~mean(.x, na.rm = TRUE), .names = "{.col}_avg")) %>%
  pivot_longer(cols = matches("_avg$"), names_to = "Video", values_to = "MEQ_Avg") %>%
   mutate(Video = as.double(str_extract(Video, "\\d+")))
cueAverages
```

```{r}
prediction_error <- study_1 %>%
  group_by(Video) %>%
  summarise(PE1_Avg = mean(PE1))
```


```{r}
normalize <- function(x) {
 ((x - min(x)) / (max(x) - min(x)))*5  # Normalizes to 0-1
}
```

```{r}
combined <- cueAverages %>%
  inner_join(prediction_error, by = "Video") %>%
  mutate(PE1_Avg = normalize(PE1_Avg))

combined %>%
  ggplot(aes(x = MEQ_Avg, y = PE1_Avg, color = Video)) +
  geom_point() +
  ylim(0,1.5)
  theme_minimal()
```

```{r}
Surprises <- study_1 %>%
  group_by(Video) %>%
  summarise(Surp = mean(Surprise_1))

cueAverages <- study_2 %>%
  #group_by(List) %>%
  summarise(across(matches("^MEQ[1-9]$|^MEQ1[0-9]$"), ~mean(.x, na.rm = TRUE), .names = "{.col}_avg")) %>%
  pivot_longer(cols = matches("_avg$"), names_to = "Video", values_to = "MEQ_Avg") %>%
   mutate(Video = as.double(str_extract(Video, "\\d+")))

combined2 <- cueAverages %>%
  inner_join(Surprises, by = "Video")

combined2 %>%
  ggplot(aes(x = Surp, y = MEQ_Avg, color = Video)) +
  geom_point()+
  theme_minimal()
```

