---
title: "D2SC ICMA Notebook"
output: html_notebook
author: "Maanav Choudhary"
date: "`r Sys.Date()`"
---

# ICMA Sept 9 2024

```{r}
plot(cars)
```
# ICMA Sept 11 2024
```{r}
ohno_this_is_a_nightmare <- "hello"
```


```{r}
2+2
```

```{r}
x <- 2+2
```
Value gets saved in environment
```{r}
?mean
```

```{r}
mean(c(1,2,3))
```
```{r}
mean(my_vector)
```

```{r}
my_vector <- c(2,3,4)
```

```{r}
?sd
sd(1:2) ^2
```

```{r}
my_numbers <- c(1,2,3,4,5,6,7,8,9,10)
getwd()
```

```{r}
my_numbers %>%
  mean()
```
```{r}
library(tidyverse)
```
# ICMA Sept 16 2024

```{r}
head(3, billboard)
```

```{r}
billboard %>%
  head(3)
```

```{r}
my_numbers <- c(1, 2, 3, 4, 5, 8, 9, 10)
```

```{r}
my_numbers %>%
  mean()

```
```{r}
mtcars %>%
  rownames_to_column()
```
```{r}
write_csv(mtcars, # object name
          "mtcars_fromR.csv" #file name to save it
          )
```

```{r}
mtcars %>%
  rownames_to_column() %>%
  write_csv("mtcars_fromR_rownames.csv")
```

```{r}
mtcars_read <- read_csv("/Users/emperormaanav/Documents/COGSCI412inR/ICMA/mtcars_fromR_rownames.csv")
```

# ICMA Sept 18 2024

```{r}
?ChickWeight
```

```{r}
ChickWeight %>%
  select(weight)
```

```{r}
ChickWeight %>%
  head(3)
```

```{r}
chick_clean <- ChickWeight %>%
  select(chick_id = Chick,
         diet = Diet,
         age_days = Time,
         weight_gm = weight)
```

```{r}
chick_clean %>%
  arrange(chick_id)
```

```{r}
chick_clean %>%
  mutate(session = case_when(TRUE         ~ as.character(age_days),
                             age_days == 0 ~ "birth",
                             age_days == 20 ~ "last1",
                             age_days == 21 ~ "last2"
                             ))
```
```{r}
chick_clean %>%
  mutate(weight_lbs = weight_gm/453.6) 
```

```{r}
chick_clean %>%
  mutate(weight_lbs = weight_gm/453.6) %>%
  group_by(diet, age_days) %>%
  summarise(N = n(),
            mean_wgt_gm = mean(weight_gm),
            mean_wgt_lbs = mean(weight_lbs)) %>%
  arrange(-age_days) %>%
  filter(age_days == 20)
```

```{r}
chick_clean %>%
  filter(age_days == 20) %>%
  mutate(weight_lbs = weight_gm/453.6) %>%
  group_by(diet) %>%
  summarise(N = n(),
            mean_wgt_gm = mean(weight_gm),
            mean_wgt_lbs = mean(weight_lbs))
```

```{r}
mtcars_modified <- read_csv("/Users/emperormaanav/Documents/COGSCI412inR/ICMA/mtcars_fromR_rownames.csv")
```
```{r}
glimpse(mtcars_modified)
```






# ICMA Sept 23 2024
 #pivot_longer(): requires data and the columns you want to pivot into long form

```{r}
head(billboard)
billboard_long <- billboard %>%
  pivot_longer(cols = starts_with("wk"),names_to = "week",names_prefix= "wk", values_to = "position",values_drop_na= TRUE)
billboard_long
```


```{r}
billboard_long %>%
  pivot_wider(names_from= week, values_from =position)
```


```{r}
billboard_sep <-billboard %>%
  separate(col = date.entered,into =c("year","month","day") ,sep = "-")
```

```{r}
billboard_sep %>%
  unite(col = "full date", c(year,month,day))

```

# ICMA Sept 25th 2024

```{r}
# Histogram of Chicks weight
ChickWeight %>%
  ggplot(aes(x = weight)) + 
  geom_histogram()
```
```{r}
ChickWeight %>%
  ggplot(aes(y = weight, x = Time, color = Diet)) +
  geom_point() +
  geom_smooth()
```
```{r}

ChickWeight %>%
  ggplot(aes(y = weight, x = Time, color = Diet)) +
  geom_point(alpha = .5) + #Transparency
  geom_smooth(se = FALSE)+ #best fits and removes confidence interval
  theme_minimal() +
  facet_grid(~Diet)+ #Splitting up into individual graphs by diet
  labs(y = "weight in grams", x = "time in days", title = "Chick Weight Over Time With Varying Diets") #Changing Axis Labels

```
# ICMA Oct 7 2024
```{r}
as.numeric("eighteen")
```
Based on your data, you must decide what you should do in this situation.


```{r}
my_double <- 12.9
```

```{r}
as.integer(my_double)
```
```{r}
as.character(my_double)
```

3. logical 
TRUE or T FALSE or F
stored as 1 and 0 resoectivly 

4. Na
2 == Na && Na == Na
both return Na bc R does not know what Na is.

5. 
and = &&
or ||
not = !

```{r}
(2.0 + 3 + 9 -4) == (2+ 6 + as.integer("2.9")) && TRUE || NA
```

# ICMA Oct 9 2024
```{r}
my_number <- 12
```
```{r}
age_data <- tribble(
                    ~ id, ~ age,
                    1, 8,
                    2, 10,
                    3, 8,
                    5, 9
            )

gender_data <- tribble(
                    ~ id, ~ gender,
                    1, "f",
                    2, "m",
                    3, "nb",
                    4, "m",
                    6, "f"
            )


gender_data_BADID <- tribble(
                    ~ id_x, ~ gender,
                    1, "f",
                    2, "m",
                    3, "nb",
                    4, "m",
                    6, "f"
            )
```

```{r}
age_data
```
```{r}
gender_data
```
```{r}
full_join(age_data, gender_data)
```
```{r}
full_join(gender_data_BADID, age_data, by = join_by(id_x == id))
```
```{r}
full_join(age_data, gender_data_BADID, by = join_by(id == id_x))
```
```{r}
right_join(age_data, gender_data)
```
```{r}
left_join(age_data, gender_data)
```

```{r}
inner_join(age_data, gender_data)
```

```{r}
bind_cols(gender_data, age_data)
```
```{r}
age_data_4 <- tribble(
                    ~ id, ~ age,
                    1, 8,
                    2, 10,
                    3, 8,
                    5, 9
            )

gender_data_4 <- tribble(
                    ~ id, ~ gender,
                    1, "f",
                    2, "m",
                    3, "nb",
                    4, "m"
            )
```

```{r}
bind_cols(age_data_4, gender_data_4)
```
```{r}
bind_rows(age_data_4, gender_data_4)
```


# ICMA Oct 16 2024

Iteration: 
iterate over people

for(var in seq){
  expr
}

```{r}
animals <- c("cat", "dog","rabbit")

for (animal in animals){
  print(animal)
}
```
```{r}
for(i in seq_along(animals)){
  print(animals[i])
}
```


```{r}
fave_number <- tribble(~name, ~number,
                       "MC", 8,
                       "AP", 9,
                       "NG", 12,
                       "VE", 6,
                       "AL", 17,
                       "AR", 3,
                       "MC", 7,
                       "RK", 8,
                       "AC", 4,
                       "SC", 21,
                       "KK", 16,
                       "RK", 28,
                       "VK", 17,
                       "MH", 12)
```

```{r}
for (i in fave_number) {
  print(i)
}
```

```{r}
class(fave_number)

```

```{r}
for (i in fave_number["number"]) {
  print(i)
}

```

```{r}
for (i in fave_number$number) {
  print(i)
}
```

```{r}
length(fave_number$number)
```

```{r}
for (i in fave_number[["number"]]) {
  print(i)
}
```

```{r}
for (i in seq_along(fave_number$name)) {
  
  print(str_c(fave_number$name[i], "'s favorite number is ", fave_number$number[i]))
  
}

```

