---
title: "D2SC ICMA Notebook"
output: html_notebook
author: "Maanav Choudhary"
date: "`r Sys.Date()`"
---

# ICMA Sept 9 2024

```{r}
plot(cars)
```

```{r}
ohno_this_is_a_nightmare <- "hello"
```


```{r}
2+2
```

```{r}
x <- 2+2
```
Value gets saved in environment
```{r}
?mean
```

```{r}
mean(c(1,2,3))
```
```{r}
mean(my_vector)
```

```{r}
my_vector <- c(2,3,4)
```

```{r}
?sd
sd(1:2) ^2
```

```{r}
my_numbers <- c(1,2,3,4,5,6,7,8,9,10)
getwd()
```

```{r}
my_numbers %>%
  mean()
```


# ICMA Sept 23 2024
 #pivot_longer(): requires data and the columns you want to pivot into long form

```{r}
library(tidyverse)
```
```{r}
head(billboard)
billboard_long <- billboard %>%
  pivot_longer(cols = starts_with("wk"),names_to = "week",names_prefix= "wk", values_to = "position",values_drop_na= TRUE)
billboard_long
```
```{r}
billboard_long %>%
  pivot_wider(names_from= week, values_from =position)
```

```{r}
billboard_sep <-billboard %>%
  separate(col = date.entered,into =c("year","month","day") ,sep = "-")
```

```{r}
billboard_sep %>%
  unite(col = "full date", c(year,month,day))

```

#ICMA Sept 25th 2024

```{r}
# Histogram of Chicks weight
ChickWeight %>%
  ggplot(aes(x = weight)) + 
  geom_histogram()
```
```{r}
ChickWeight %>%
  ggplot(aes(y = weight, x = Time, color = Diet)) +
  geom_point() +
  geom_smooth()
```
```{r}

ChickWeight %>%
  ggplot(aes(y = weight, x = Time, color = Diet)) +
  geom_point(alpha = .5) + #Transparency
  geom_smooth(se = FALSE)+ #best fits and removes confidence interval
  theme_minimal() +
  facet_grid(~Diet)+ #Splitting up into individual graphs by diet
  labs(y = "weight in grams", x = "time in days", title = "Chick Weight Over Time With Varying Diets") #Changing Axis Labels

```
#ICMA Oct 7 2024
```{r}
as.numeric("eighteen")
```
Based on your data, you must decide what you should do in this situation.


```{r}
my_double <- 12.9
```

```{r}
as.integer(my_double)
```
```{r}
as.character(my_double)
```

3. logical 
TRUE or T FALSE or F
stored as 1 and 0 resoectivly 

4. Na
2 == Na && Na == Na
both return Na bc R does not know what Na is.

5. 
and = &&
or ||
not = !

```{r}
(2.0 + 3 + 9 -4) == (2+ 6 + as.integer("2.9")) && TRUE || NA
```

#ICMA Oct 16 2024

Iteration: 
iterate over people

for(var in seq){
  expr
}

```{r}
animals <- c("cat", "dog","rabbit")

for (animal in animals){
  print(animal)
}
```
```{r}
for(i in seq_along(animals)){
  print(animals[i])
}
```


