---
title: "DE2_Day1"
output: html_notebook
uthor: "Maanav Choudhary"
date: "`r Sys.Date()`"
---
```{r}
library(tidyverse)
```

```{r}
files <- list.files(path = "/Users/emperormaanav/Documents/COGSCI412inR/DE2/DE2_Parker_UNZIP-BEFORE-USING/jumping_data_parker/",
                    pattern = "*.csv",
                    full.names = TRUE)
```


```{r}
convert_cols <- function(file){
  file <- file %>%
    mutate(sex = case_when(sex == FALSE ~ "F",
                         sex == "M" ~ "M"),
          date = as.character(date))
  
}
```

```{r}
raw_data <- map(files, read_csv)%>%
  map(convert_cols) %>%
  bind_rows()
```

Mao maps a certain functino to the values in the first paramater
```{r}
raw_data %>%
  group_by(subject,distance)%>%
  #filter(outcome != 2)
  mutate(succ_rate_NOabort = sum(outcome ==1)/n())
```


```{r}
raw_data [[1]] %>%
  mutate(sex = case_when(sex == FALSE ~ "F",
                         TRUE ~ sex))
```

```{r}
raw_data %>%
  distinct()
```

## exploring the data

```{r}
summary_raw_data <- raw_data %>%
  group_by(distance, subject) %>%
  summarise(succ_rate = sum(outcome == 1)/n())
```

```{r}
summary_raw_data %>%
  ggplot(aes(x = succ_rate))+
  geom_histogram()
```

```{r}
summary_raw_data %>%
  ggplot(aes(x = distance, 
             y = succ_rate,
             group = subject))+
  geom_line() +
  ylim(0,1)
```


Replicating figure in the paper
outcome is discrete between values of 0, 1, and 2. The plot is continuous between 0 and 1

```{r}
raw_data %>%
  group_by(subject, distance) %>%
# filter(outcome == 1 | outcome == 0)
# filter(outcome != 2) 
  filter(outcome %in% c(0, 1)) %>%
  summarise(succ_rate = sum(outcome == 1)/n()) %>%
  ggplot(aes(x = distance,
             y = succ_rate,
             group = subject)) +
  geom_line() +
  ylim(0, 1)
```

## Day 2

Three goals:
1. Make our plot look like theirs
2. Explore diff features of the dataset 
3. Make a presentation of the new ffeature we wanna explore - fuck allat

## Make our plot look like theirs

```{r}
raw_data %>%
  group_by(subject, distance) %>%
# filter(outcome == 1 | outcome == 0)
# filter(outcome != 2) 
  filter(outcome %in% c(0, 1)) %>%
  summarise(succ_rate = sum(outcome == 1)/n()) %>%
  ggplot(aes(x = distance,
             y = succ_rate)) +
  geom_line(aes(group = subject), alpha = .3, color = "darkblue") +
  stat_summary(fun.data = "mean_se", geom = "errorbar",width = .2, color = "darkblue")+
  stat_summary(fun.y = mean, geom= "line" , color = "darkblue")+
  ylim(0, 1)+
  xlim(10, 25)+
    labs(x = "gap distamce (cm)",
         y = "success rate")+
  theme(panel.background =  element_rect(fill = "white"), axis.line = element_line(color = "grey"))+
  annotate(geom = "text", label = "binocular", x = 11, y = .1, color = "darkblue")
```

## Explore new feature

```{r}
raw_data %>%
  distinct(experimenter)
```
```{r}
raw_data %>%
  group_by(subject, experimenter) %>%
  filter(outcome %in% c(0,1)) %>%
  summarise(succ_rate = sum(outcome ==1)/n()) %>%
  ggplot(aes(y = succ_rate, x = experimenter)) +
  geom_jitter(alpha = .3, width = .2,height = 0) + 
  ylim(0,1)
```


