---
title: "D2SC: Weekly Assignments"
author: "Maanav Choudhary"
date: "2024-09-13"
output: html_notebook
---

# Initial Loading

```{r}
library(tidyverse)
```


# Week 1
In order to figure out how to load the tidyverse package, I went to the tidyverse docsumentation. I typed in "How to load tidyverse in R" in google.

I chose the first link that came up : https://tidyverse.tidyverse.org/

I then ran the code chunk to check for errors and make sure it was working.

```{r}
?tidyverse
```

tidyverse-package {tidyverse}	R Documentation
tidyverse: Easily Install and Load the 'Tidyverse'
Description
logo
The 'tidyverse' is a set of packages that work in harmony because they share common data representations and 'API' design. This package is designed to make it easy to install and load multiple 'tidyverse' packages in a single step. Learn more about the 'tidyverse' at https://www.tidyverse.org.

Author(s)
Maintainer: Hadley Wickham hadley@rstudio.com

Other contributors:

RStudio [copyright holder, funder]

See Also
Useful links:

https://tidyverse.tidyverse.org

https://github.com/tidyverse/tidyverse

Report bugs at https://github.com/tidyverse/tidyverse/issues

[Package tidyverse version 2.0.0 Index]


# Week 2

```{r}
analogyDataset <- read.csv("tidy_data/MFIndD_analogy.csv")
print(analogyDataset)
```

1. In this data set, the first column, named "qualtrics_id", contains the unqiue identifier for the particpants. 

2.

a. There are 792 rows in the data set, and 6 columns. I did not need to write a seperate code chunk for this, as printing the analogyDataset shows the dimensions of it in the description. 

```{r}
# b.
?dplyr_by
participants <- distinct(analogyDataset["qualtrics_id"])
print(participants)
```
There are 99 unqiue people in the dataset. I found this by using the dplyr function "distinct" on the particpant Ids, the size of the returned vector is the amount of people particpating in the study.

```{r}
# c
participant_trials <- analogyDataset %>%
  group_by(qualtrics_id) %>%
    summarize(max_trials = max(trial_number))

summarize(participant_trials, sd(max_trials))

```
Yes, every particpant has data from the same number of trials. I got the max of each participants trials, and took the standard deviation of them. The standard deviation being 0 represents that all participants have the same maximum number of trials. 



