---
title: "D2SC: Weekly Assignments"
author: "Maanav Choudhary"
date: "2024-09-13"
output: html_notebook
---

# Initial Loading

```{r}
library(tidyverse)
```


# Week 1
In order to figure out how to load the tidyverse package, I went to the tidyverse docsumentation. I typed in "How to load tidyverse in R" in google.

I chose the first link that came up : https://tidyverse.tidyverse.org/

I then ran the code chunk to check for errors and make sure it was working.

```{r}
?tidyverse
```

tidyverse-package {tidyverse}	R Documentation
tidyverse: Easily Install and Load the 'Tidyverse'
Description
logo
The 'tidyverse' is a set of packages that work in harmony because they share common data representations and 'API' design. This package is designed to make it easy to install and load multiple 'tidyverse' packages in a single step. Learn more about the 'tidyverse' at https://www.tidyverse.org.

Author(s)
Maintainer: Hadley Wickham hadley@rstudio.com

Other contributors:

RStudio [copyright holder, funder]

See Also
Useful links:

https://tidyverse.tidyverse.org

https://github.com/tidyverse/tidyverse

Report bugs at https://github.com/tidyverse/tidyverse/issues

[Package tidyverse version 2.0.0 Index]


# Week 2

```{r}
analogyDataset <- read.csv("tidy_data/MFIndD_analogy.csv")
print(analogyDataset)
```

1. In this data set, the first column, named "qualtrics_id", contains the unqiue identifier for the particpants. 

2.

a. There are 792 rows in the data set, and 6 columns. I did not need to write a seperate code chunk for this, as printing the analogyDataset shows the dimensions of it in the description. 

```{r}
# b.
?dplyr_by
participants <- distinct(analogyDataset["qualtrics_id"])
print(participants)
```
There are 99 unqiue people in the dataset. I found this by using the dplyr function "distinct" on the particpant Ids, the size of the returned vector is the amount of people particpating in the study.

```{r}
# c
participant_trials <- analogyDataset %>%
  group_by(qualtrics_id) %>%
    summarize(max_trials = max(trial_number))

summarize(participant_trials, sd(max_trials))

```
Yes, every particpant has data from the same number of trials. I got the max of each participants trials, and took the standard deviation of them. The standard deviation being 0 represents that all participants have the same maximum number of trials. 




# Week 3

 Process.)
 
```{r, eval = FALSE}
analogyDataset %>%
  summarize(.by = qualtrics_id, .groups = response_type, el_count = n("Rel"), )
#analogyDataset %>%
  #pivot_wider(id_cols =c(qualtrics_id), names_from = match_type_1, values_from = response_type)
```
The code chunk above was one of my attempts at solving question 1. I was correct in using the summarize function, however the syntax I used in the statement was not correct. The use of .by was correct. Grouping the info by qualtrics_id was what the question wanted, and resulted in the correct result for the code chunk that was my final solution. However, I was not properly understanding the use of .groups. I was getting an error for response_type. I double checked and saw the spelling of it was correct, so I went to the help part of R studio and saw that .groups was used more for things like groping rowwise rather than by specific data. I then googled counting with summarize and saw that the sum() function was better than n() which is the function I was seeing in the help tab. After realizing that and playing around with the syntax, I was able to get the desired result from the code chunk below. 

1.)

```{r}
summarised_by_rel_matches <- analogyDataset %>%
  summarize(.by = qualtrics_id, rel = sum(response_type == "Rel", na.rm = TRUE) )
```

2.)

```{r}
summarised_by_rel_matches %>%
  ggplot(aes(x = rel))+
  geom_histogram()+
  labs(y = "Number of participants", x = "Number of trials with relational Matches")

```
I notice that the variable of relational match count is not spread in an even way. The variable is more dense around the ends. Many of the participants have either 8 relational matches, meaning they select a relational match in every trial, or 0 relational matches, meaning they select relational matches in none of the trials. 

3.)

```{r}
analogyDataset%>% 
  pivot_wider(id_cols = c(qualtrics_id), names_from = "trial_number",names_sort = TRUE,values_from = "response_type" )
```

# Week 4


```{r}
rei_dataset <- read.csv("tidy_data/MFIndD_REI.csv")
head(rei_dataset)
```
The type of the response column is char, while the type of the scored_response column is an int. The reason that the response column has type char, is because although it includes some numbers, it also contains some cells that include, "strongly agree" or other examples of non numeric entries.

2.)
```{r}
rei_dataset_adjusted <- rei_dataset %>%
  mutate(response = case_when(response == "Strongly Disagree" ~ 1.0,response == "Strongly Agree" ~ 5.0 , is.na(response) == TRUE ~ 0, TRUE ~ as.double(response)))
#Printing adjusted data to ensure it worked
rei_dataset_adjusted
```

3.)
```{r}
rei_analysis <- rei_dataset_adjusted %>%
  mutate(new_scored_response = case_when(rev_scoring == "neg" ~ 6-response, TRUE ~ response))
#Printing the data set to show the new column
rei_analysis
```
Putting out the inputs and outputs of the numbers when reverse scoring is neg to find a pattern.
1 -> 5
2 -> 4
3 ->3
4 ->2
5 ->1
After looking for a while, i noticed that 6-input is equal to the correct output for all of our possible inputs.

4.)
```{r}
accuracy <- rei_analysis%>%
summarise(all(new_scored_response == scored_response, na.rm = TRUE))
accuracy
```
I used summarize to compare the new scored response column with the one already in the data set, if they are all equal, then the code should return True. The return of True indicates that the new_scored_responsse column is correct.

# Week 5

1a.)
```{r}
rei_sub_scale_summary <- rei_analysis %>%
  group_by(qualtrics_id, sub_type ) %>%
  summarize(score = sum(new_scored_response))
rei_sub_scale_summary
```

1b.)
```{r}
rei_sub_scale_summary %>%
  ungroup() %>%
  summarise(any(is.na(score)))
```

I ungrouped here first because i was getting a response that was not correct, any() should result in one boolean yet i was getting a whole column. I went to stack overflow for this. After ungrouping, i did any() which would return TRUE if any of the score values were na. The return of false indicates that there were no NA values.

1c.)

My code did not show any values that were na, however if there were i would have to go and look back at the code for any place i could add an na.rm = TRUE to ignore the na values for that calculation and/or summary.

2.)
```{r}
analogy_rei_joint <- full_join(summarised_by_rel_matches, rei_sub_scale_summary)
analogy_rei_joint
```

3.)
```{r}
analogy_rei_joint %>%
  ggplot(aes(y = score , x= rel, color = sub_type))+
  geom_point() +
  geom_smooth(se=FALSE) +
  theme_minimal() +
  labs(y = "REI Score", x = "number of relational matches", title = "Correlation between relational matches, score, and sub type")
```

