---
title: "D2SC: Weekly Assignments"
author: "Maanav Choudhary"
date: "2024-09-13"
output: html_notebook
---

# Initial Loading

```{r}
library(tidyverse)
```


# Week 1
In order to figure out how to load the tidyverse package, I went to the tidyverse docsumentation. I typed in "How to load tidyverse in R" in google.

I chose the first link that came up : https://tidyverse.tidyverse.org/

I then ran the code chunk to check for errors and make sure it was working.

```{r}
?tidyverse
```

tidyverse-package {tidyverse}	R Documentation
tidyverse: Easily Install and Load the 'Tidyverse'
Description
logo
The 'tidyverse' is a set of packages that work in harmony because they share common data representations and 'API' design. This package is designed to make it easy to install and load multiple 'tidyverse' packages in a single step. Learn more about the 'tidyverse' at https://www.tidyverse.org.

Author(s)
Maintainer: Hadley Wickham hadley@rstudio.com

Other contributors:

RStudio [copyright holder, funder]

See Also
Useful links:

https://tidyverse.tidyverse.org

https://github.com/tidyverse/tidyverse

Report bugs at https://github.com/tidyverse/tidyverse/issues

[Package tidyverse version 2.0.0 Index]


# Week 2

```{r}
analogyDataset <- read.csv("tidy_data/MFIndD_analogy.csv")
print(analogyDataset)
```

1. In this data set, the first column, named "qualtrics_id", contains the unqiue identifier for the particpants. 

2.

a. There are 792 rows in the data set, and 6 columns. I did not need to write a seperate code chunk for this, as printing the analogyDataset shows the dimensions of it in the description. 

```{r}
# b.
?dplyr_by
participants <- distinct(analogyDataset["qualtrics_id"])
print(participants)
```
There are 99 unqiue people in the dataset. I found this by using the dplyr function "distinct" on the particpant Ids, the size of the returned vector is the amount of people particpating in the study.

```{r}
# c
participant_trials <- analogyDataset %>%
  group_by(qualtrics_id) %>%
    summarize(max_trials = max(trial_number))

summarize(participant_trials, sd(max_trials))

```
Yes, every particpant has data from the same number of trials. I got the max of each participants trials, and took the standard deviation of them. The standard deviation being 0 represents that all participants have the same maximum number of trials. 




# Week 3

 Process.)
 
```{r, eval = FALSE}
analogyDataset %>%
  summarize(.by = qualtrics_id, .groups = response_type, el_count = n("Rel"), )
#analogyDataset %>%
  #pivot_wider(id_cols =c(qualtrics_id), names_from = match_type_1, values_from = response_type)
```
The code chunk above was one of my attempts at solving question 1. I was correct in using the summarize function, however the syntax I used in the statement was not correct. The use of .by was correct. Grouping the info by qualtrics_id was what the question wanted, and resulted in the correct result for the code chunk that was my final solution. However, I was not properly understanding the use of .groups. I was getting an error for response_type. I double checked and saw the spelling of it was correct, so I went to the help part of R studio and saw that .groups was used more for things like groping rowwise rather than by specific data. I then googled counting with summarize and saw that the sum() function was better than n() which is the function I was seeing in the help tab. After realizing that and playing around with the syntax, I was able to get the desired result from the code chunk below. 

1.)

```{r}
summarised_by_rel_matches <- analogyDataset %>%
  summarize(.by = qualtrics_id, rel = sum(response_type == "Rel", na.rm = TRUE) )
```

2.)

```{r}
summarised_by_rel_matches %>%
  ggplot(aes(x = rel))+
  geom_histogram()+
  labs(y = "Number of participants", x = "Number of trials with relational Matches")

```
I notice that the variable of relational match count is not spread in an even way. The variable is more dense around the ends. Many of the participants have either 8 relational matches, meaning they select a relational match in every trial, or 0 relational matches, meaning they select relational matches in none of the trials. 

3.)

```{r}
analogyDataset%>% 
  pivot_wider(id_cols = c(qualtrics_id), names_from = "trial_number",names_sort = TRUE,values_from = "response_type" )
```

