---
title: "D2SC: Weekly Assignments"
author: "Maanav Choudhary"
date: "2024-09-13"
output: html_notebook
---

# Initial Loading

```{r}
library(tidyverse)
```


# Week 1
In order to figure out how to load the tidyverse package, I went to the tidyverse docsumentation. I typed in "How to load tidyverse in R" in google.

I chose the first link that came up : https://tidyverse.tidyverse.org/

I then ran the code chunk to check for errors and make sure it was working.

```{r}
?tidyverse
```

tidyverse-package {tidyverse}	R Documentation
tidyverse: Easily Install and Load the 'Tidyverse'
Description
logo
The 'tidyverse' is a set of packages that work in harmony because they share common data representations and 'API' design. This package is designed to make it easy to install and load multiple 'tidyverse' packages in a single step. Learn more about the 'tidyverse' at https://www.tidyverse.org.

Author(s)
Maintainer: Hadley Wickham hadley@rstudio.com

Other contributors:

RStudio [copyright holder, funder]

See Also
Useful links:

https://tidyverse.tidyverse.org

https://github.com/tidyverse/tidyverse

Report bugs at https://github.com/tidyverse/tidyverse/issues

[Package tidyverse version 2.0.0 Index]

